**The Role of Interoception and Theory of Mind in Deception**

### 2022-10-10 index.Rmd
fig 2

>>>>

# Deception Trait {.tabset}

## Confidence

```{r message=FALSE, warning=FALSE}
results <- list()
for (var in c("LIE_Ability", "LIE_Frequency", "LIE_Contextuality", "LIE_Negativity")) {
  model <- brms::brm(as.formula(paste0(
    "Confidence ~ Answer / (Condition / ",
    var,
    ") + (1|Participant) + (1|Item)"
  )),
  data = df, family = "beta", refresh = 0, seed=3, iter = 4000,
  prior = set_prior("student_t(1, 0, 1)", class = "b")
  )

display(format_table(results$LIE_Ability, stars = TRUE))
display(format_table(results$LIE_Frequency, stars = TRUE))
display(format_table(results$LIE_Contextuality, stars = TRUE))
display(format_table(results$LIE_Negativity, stars = TRUE))
```

## RT

```{r message=FALSE, warning=FALSE}
results <- list()
for (var in c("LIE_Ability", "LIE_Frequency", "LIE_Contextuality", "LIE_Negativity")) {
  model <- brms::brm(as.formula(paste0(
    "RT ~ Answer / (Condition / ",
    var,
    ") + (1|Participant) + (1|Item)"
  )),
  data = df, refresh = 0, seed=3, iter = 4000,
  prior = set_prior("student_t(1, 0, 3)", class = "b")
  )

display(format_table(results$LIE_Ability, stars = TRUE))
display(format_table(results$LIE_Frequency, stars = TRUE))
display(format_table(results$LIE_Contextuality, stars = TRUE))
display(format_table(results$LIE_Negativity, stars = TRUE))
```

## Heart Rate

```{r message=FALSE, warning=FALSE}
results <- list()
for (var in c("LIE_Ability", "LIE_Frequency", "LIE_Contextuality", "LIE_Negativity")) {
  model <- brms::brm(as.formula(paste0(
    "HeartRate ~ Answer / (Condition / ",
    var,
    ") + (1|Participant) + (1|Item)"
  )),
  data = df, refresh = 0, seed=3, iter = 4000,
  prior = set_prior("student_t(1, 0, 8)", class = "b")
  )

display(format_table(results$LIE_Ability, stars = TRUE))
display(format_table(results$LIE_Frequency, stars = TRUE))
display(format_table(results$LIE_Contextuality, stars = TRUE))
display(format_table(results$LIE_Negativity, stars = TRUE))
```
